Tor's Usability for Censorship Circumvention

### 2015-12-10 paper/circumvention-experiment.tex
added a figure on visualizing participant workflows

One exciting analysis we will perform is to build a Markov model of the UI flow chart (like the one seen in Figure \ref{fig:interface}). We believe that this will be helpful in communicating participant behavior in aggregate since it will show the change in the UI flow structure, as well as how participants decisions have changed (e.g., in the old interface, a participant in a censorship environment which does not block Tor has a 0.4 chance of choosing ``connect,'' whereas in the new interface, the probability is 0.6). We have other visualizations in mind, such as displaying the number of windows traversed by each participant as a bar graph.\\

>>>>

One exciting analysis we will perform is to build a Markov model of the UI flow chart (like the one seen in Figure \ref{fig:interface}). We believe that this will be helpful in communicating participant behavior in aggregate since it will show the change in the UI flow structure, as well as how participants decisions have changed (e.g., in the old interface, a participant in a censorship environment which does not block Tor has a 0.4 chance of choosing ``connect,'' whereas in the new interface, the probability is 0.6). We have other visualizations in mind to display all participants' window traversal at a glance (Figure \ref{fig:bar} shows an illustration), as well as other analyses.\\

\begin{figure}[t]
\label{fig:bar}
  \centering
    \includegraphics[width=0.5\textwidth]{screen-bar.png}
    \caption{An illustration of how we plan to visualize large-scale UI flows as a succinct way to display all participants' window traversal. We plan to color code the screens so that the reader can see trends at a glance, such as how the UI path for participants in a mild censorship environment with the old design compare to the UI flow for the participants in a mild censorship environment with a new design. It also can communicate how much work was required of a user to configure a connection.}
\end{figure}
